Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-25 paper/paper.tex
pass on fixes

The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc{} defines a function with a tail-call
recursion. The test fails in all engines but \jsc{}, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} does not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}.
%% \Mar{igor,
%%   nao consigo entender o porque deste caso nao dar aqueles erros
%%   (ReferenceError/TypeError) que vc. me mostrou e estourar na
%%   assercao. explique e de um exemplo concreto, por favor$\rightarrow$
%% }
%% \Igor{Ha testes em que o non-standard element aparece com a mensagem de erro
%% diferente da que usamos anteriormente. Por exemplo, existem testes que 
%% estao dentro de um bloco try/catch, mesmo se a linha quebrar, 
%% o catch vai capturar e enviar uma mensagem tipo "expected true, got false".
%% }
\textbf{Non-Standard Element.} These cases manifest when a function or
an object property is undefined in the execution engine but we were
unable to capture looking for error types like \CodeIn{ReferenceError}
and \CodeIn{TypeError}. For example, we found cases where the test (or
its harness) capture the corresponding exception, making the test to
fail in an assertion instead. \Mar{igor, ha alguma explicacao/intuicao
  para explicar porque nao conseguir classificar isto?.$\rightarrow$}
\Igor{Exemplos: Testes especificos do engenho que }\Mar{nao
  entendi. isto nao acabaria quebrando por um dos motivos anteriores?
  seja mais especifico, por favor!}  \textbf{Unknown.} This category
includes the cases we were unable to confidently diagnose the failure
but we suspected it was a false alarm.

@@

Considering severity levels, it is worth noting that \jsc{} uses five
levels~\cite{jsc-severity} whereas \chakra{}~\cite{chakra-severity}
and \smonkey{}~\cite{mozilla-severity} use only three\Mar{e v8?}. As
usual, the smallest the severity value the highest the severity of the
bug. We use a dash (``-'') in place of the severity level for the
cases where the bug report is pending confirmation.\Mar{por favor,
  corrija estes numeros *com cuidado*! se possivel, use macros.} Of
the \Fix{17} bugs we reported in this experiment, \Fix{9} were
promoted from the status ``New'' to ``Confirmed''. Of these, \Fix{8}
are severity-2 bugs.  Although we did not find any showstopper
critical bugs, most of the bugs are seemingly important as per the
categorization given by engineers. Analyzing the issue tracker of
\chakra, we found that severity-1 bugs are indeed rare. Considering
the bugs confirmed by developers, \chakra{} was the engine with the
highest number, \Fix{8} in total, with \Fix{1} bug fixed. Considering
the remaining engines, \veight{} developers confirmed \Fix{two} of the
\Fix{three} bug we reported, fixing \Fix{one}. Curiously, Google
engineers confirmed the report we issued in a few hours. We found that
development teams of other engines, specially \jsc\, took much longer
to analyze bug reports as can be observed in the \jsc\ stacked bar
from Figure~\ref{fig:stacked-engine}.

@@

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of two new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications. The source ``Error Message Mismatch''
indicates that \Mar{por favor, explique. nao consigo lembrar.}
\Igor{existem testes que realizam a comparacao de strings, o fuzzer pode
alterar o corpo da mensagem. Esta era a ideia, mas 
casos onde o fuzzer muda a msg em uma assercao 
(por exempo 'assertThrows(SyntaxError(), "SyntaxError: syntax error")') 
todos os engenhos falham e o teste nao ser reportado caso alcance esse bloco.
Porem, existem casos em que o teste falha por message mismatch, 
mas a discrepancia ocorre no engenho que nao exibe essa mensagem. 
Analisando os casos que encontramos dessa natureza, 
a comparacao da mensagem aparece no report, 
porem a discrepancia ocorre quando o teste nao mostra 
essa mensagem (passa por motivos de invalid input). 
Eu classifiquei como message mismatch, 
mas creio que nesse caso seria invalid input. Pq se for message mis
}

@@

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4.}\Mar{de que tabela?} The JS code \CodeIn{\{var a =
  \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
  assert(+a === 0)\}} manifested a bug in the \js{} engine \chakra{}.
The object property \CodeIn{valueOf} stores a function that returns a
primitive value identifying the target object~\cite{valueof}. The
original version of this code returns an empty string whereas the
version of the code modified by the Radamsa fuzzer~\cite{radamsa}
returns a string representation of a null character (\CodeIn{NUL} in ascii). The unary plus expression ``\CodeIn{+a}",
used in the assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
  chakra did that it would be fine, no?} evaluates the unary
plus to NaN as expected, as the null character cannot be converted. As
result, the test fails as expected. \chakra{}, in contrast,
incorrectly converts the string to zero, making the test to pass. All
other engines fail on this test. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.

>>>>

The sources of false positives found in this experiment are as
follows: \textbf{Undefined Behavior.} False positives of this kind are
manifested when tests cover implementation-dependent behavior, as
defined in the ECMA262 specification~\cite{ecmas262-spec}. For
example, one of the tests from \jerry\ uses the function
\CodeIn{Number.toPrecision([precision])}, which translates a number to
a string, considering a given number of significant digits. The
floating-point approximation of the real value is
implementation-dependent, making that test to pass only in
\chakra. \textbf{Timeout/OME\footnote{ome is for out of memory
    error.}.} False positives of this kind typically manifest when the
engine that runs the test does not optimize the code as the original
engine of the test. As result, the test fails to finish at the
specified time budget or it exceeds the memory budget. For example, a
test case from \jsc{} defines a function with a tail-call
recursion. The test fails in all engines but \jsc{}, which implements
tail-call optimization. \textbf{Not implemented.} False positives of
this kind manifest when a test fails because it covers a function that
is part of the official spec, but is not implemented in the target
engine yet. For example, at the time of writing, \chakra{} does not
implement by default various properties from the \mcodeid{Symbol}
object. These properties are only available activating the ES6
experimental mode with the flag \CodeIn{-ES6Experimental}.
%% \Mar{igor,
%%   nao consigo entender o porque deste caso nao dar aqueles erros
%%   (ReferenceError/TypeError) que vc. me mostrou e estourar na
%%   assercao. explique e de um exemplo concreto, por favor$\rightarrow$
%% }
%% \Igor{Ha testes em que o non-standard element aparece com a mensagem de erro
%% diferente da que usamos anteriormente. Por exemplo, existem testes que 
%% estao dentro de um bloco try/catch, mesmo se a linha quebrar, 
%% o catch vai capturar e enviar uma mensagem tipo "expected true, got false".
%% }
\textbf{Non-Standard Element.} These cases manifest when a function or
an object property is undefined in the execution engine but we were
unable to capture looking for error types like \CodeIn{ReferenceError}
and \CodeIn{TypeError}. For example, we found cases where the test (or
its harness) capture the corresponding exception, making the test to
fail in an assertion instead. \Mar{igor, ha alguma explicacao/intuicao
  para explicar porque nao conseguir classificar isto?.$\rightarrow$}
  \Igor{Exemplos: Testes especificos e/ou com entradas invalidas, 
  por exemplo cobre uma especificacao antiga onde o
  teste esperava uma propriedade true, mas na documentacao 
  cita que a propriedade tem que ser false.}\Mar{nao
  entendi. isto nao acabaria quebrando por um dos motivos anteriores?
  seja mais especifico, por favor!}  \textbf{Unknown.} This category
includes the cases we were unable to confidently diagnose the failure
but we suspected it was a false alarm.

@@

Considering severity levels, it is worth noting that \jsc{}~\cite{jsc-severity} 
and \smonkey{}~\cite{mozilla-severity} uses five levels, 
whereas \chakra{}~\cite{chakra-severity} and \veight{}~\cite{v8-severity} 
use only three. As usual, the smallest the severity value the 
highest the severity of the bug. We use a dash (``-'') 
in place of the severity level for the cases where the bug 
report is pending confirmation.\Mar{por favor,
  corrija estes numeros *com cuidado*! se possivel, use macros.} Of
the \Fix{17} bugs we reported in this experiment, \Fix{9} were
promoted from the status ``New'' to ``Confirmed''. Of these, \Fix{8}
are severity-2 bugs.  Although we did not find any showstopper
critical bugs, most of the bugs are seemingly important as per the
categorization given by engineers. Analyzing the issue tracker of
\chakra, we found that severity-1 bugs are indeed rare. Considering
the bugs confirmed by developers, \chakra{} was the engine with the
highest number, \Fix{8} in total, with \Fix{1} bug fixed. Considering
the remaining engines, \veight{} developers confirmed \Fix{two} of the
\Fix{three} bug we reported, fixing \Fix{one}. Curiously, Google
engineers confirmed the report we issued in a few hours. We found that
development teams of other engines, specially \jsc\, took much longer
to analyze bug reports as can be observed in the \jsc\ stacked bar
from Figure~\ref{fig:stacked-engine}.

@@

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. The sources of imprecision are as defined in
Section~\ref{sec:transplantation} with the addition of two new
sources, which we did not observe before. These sources are
highlighted with a ``*'' in the table. The source ``Invalid Input''
indicates that the test input violated some part of the
specification. For example, the test indirectly invoked some function
with unexpected arguments; this happens because fuzzing is not
sensitive to function specifications. The source ``Error Message Mismatch''
indicates that \Mar{por favor, explique. nao consigo lembrar.}
\Igor{existem testes que realizam a comparacao de strings, o fuzzer pode
alterar o corpo da mensagem. Esta era a ideia, mas 
casos onde o fuzzer muda a msg em uma assercao 
(por exempo 'assertThrows(SyntaxError(), "SyntaxError: syntax error")') 
todos os engenhos falham e o teste nao ser reportado caso alcance esse bloco.
Porem, existem casos em que o teste falha por message mismatch, 
mas a discrepancia ocorre no engenho que nao exibe essa mensagem. 
Analisando os casos que encontramos dessa natureza, 
a comparacao da mensagem aparece no report, 
porem a discrepancia ocorre quando o teste nao mostra 
essa mensagem (passa por motivos de invalid input).
Eu classifiquei como message mismatch, 
mas creio que nesse caso seria invalid input.
}

@@

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:cross-testing}.} 
The JS code \CodeIn{\{var a =
  \{valueOf:~function()\{} \CodeIn{return ``\textbackslash{}x00''\}\}
  assert(+a === 0)\}} manifested a bug in the \js{} engine \chakra{}.
The object property \CodeIn{valueOf} stores a function that returns a
primitive value identifying the target object~\cite{valueof}. The
original version of this code returns an empty string whereas the
version of the code modified by the Radamsa fuzzer~\cite{radamsa}
returns a string representation of a null character (\CodeIn{NUL} in ascii). The unary plus expression ``\CodeIn{+a}",
used in the assertion, is equivalent to the operation
\CodeIn{ToNumber(a.valueOf())} that converts a string to a number,
otherwise the operation returns NaN (Not a
Number)\cite{unary-plus}. For this case, \chakra{}\Mar{\chakra? if
  chakra did that it would be fine, no?} evaluates the unary
plus to NaN as expected, as the null character cannot be converted. As
result, the test fails as expected. \chakra{}, in contrast,
incorrectly converts the string to zero, making the test to pass. All
other engines fail on this test. As Table~\ref{tab:bugs} shows, the
\chakra{} team fixed the issue soon after we reported the problem.
